% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Edward Parry}
% \address used twice to have two lines of address
\address{61 Jim Driscoll Way, Cardiff, CF11 7JL}
\address{+44 (0) 78927 18071\\me@edparry.com\\edparry.com}

 
\begin{resume}
 
\section{PROFILE}A highly motivated and enthusiastic undergraduate student who is on target to achieve a 2:1 in Computer Science from Aberystwyth University, has significant experience in web technologies such as C\#, jQuery, (X)HTML \& CSS, XSLT, alongside an ever-expanding interest of networking administration and security, and is currently working as an IT Consultant at Method4 in Cardiff.

\section{KEY SKILLS}
{\bf Solid team working ability} Demonstrated through multiple group programming projects, team sports and musical ensembles.\\
{\bf Competent in (X)HTML, CSS \& SQL} Several years of personal experience of designing and developing personal and small-business websites, supported by {\sl Introduction to Web Development} and {\sl Interactive Web Programming} modules.\\
%{\bf Strong knowledge of Apple products} Through three years of writing Apple coverage in which I have had to keep up to date with Apple's entire product line and new and future releases.
{\bf Working knowledge of PHP \& JavaScript} Gained 80\% in a {\sl Introduction to Web Development} module which included JavaScript, and currently studying PHP scripting to more depth in a second-year course.\\
{\bf Hardware \& Server Maintenance} Able to maintain, update and administrate computer hardware and architecture, along with server hardware and the ability to build a web server from a standard Linux machine and to optimize it.\\
{\bf Working knowledge of Java} Gained through four modules which include various teaching methods and individual and group assignments to ensure a thorough understanding.\\
{\bf Excellent Experience with OS X, Linux, Unix \& Windows NT} Proficient knowledge of the Mac OS X operating system, along with a decent understanding of Windows NT, Linux \& Unix-based solutions.\\
{\bf Knowledge of Perl} Completed a short course in the Perl language, and have noted similarities between other languages which is allowing a further understanding into practical uses for the language.
 
\section{EDUCATION} {\bf University of Wales, Aberystwyth} \hfill September 2010 - Present\\
               Computer Science, BSc | {\sl Expected, 2:1}\\
Key modules: 
\begin{itemize} \itemsep -2pt
\item Web Development Tools: 80\%, Web Programming: 72\%
\item Introduction to Computer Hardware, Operating Systems \& Unix Tools: 67\%
\item Introduction to System and Network Services Administration: 71\%
\item Software Development: 63\%\\
\end{itemize}
{\bf Blythe Bridge High School \& Sixth Form} \hfill September 2003 - June 2010 \\ \\
{\bf A-Levels} Computing, Music\\
{\bf AS-Levels} Mathematics \& Mechanics, Physics, Business Studies\\
{\bf 14 GCSEs} including, Mathematics, English Language, IT \& Business Communications Technology (achieved a year early at A grade).

\newpage
\section{EMPLOYMENT}
	{\sl IT Consultant} \hfill July 2012 - Present \\
	Method4, Cardiff
	\begin{itemize} \itemsep -2pt
		\item Working with various technologies including C\# (.Net), jQuery, XSLT \& XML, Microsoft SourceSafe, and content management systems such as Umbraco to work towards effective solutions to technical problems for a range of clients from both the public and private sectors.
		\item Gained valuable experience with client interaction and communication skills.
		\item An industrial year position as part of my computer science degree at Aberystwyth University.
	\end{itemize}

	{\sl Web \& IT Manager} \hfill April 2011 - June 2012 \\
	The Courier, Aberystwyth's Student Newspaper
	\begin{itemize} \itemsep -2pt
	\item Responsible for maintaining The Courier's website and social networking presence.
	\item Assisting committee members or contributors with any technical difficulties, and working with the online editors to support editorial functions.
	\end{itemize}

	       {\sl Staff Writer} \hfill January 2009 - June 2012 \\
                North American Publishing Company, Appletell.com
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Stay on the fore-front of the technology sector, in particular Apple Inc and surrounding companies.
	       \item Writing high quality articles to often very tight deadlines in breaking news situations.
	       \item Consistently produce a high standard of writing of news, reviews and original opinion articles.
                \end{itemize}
 
              {\sl Administrative Assistant} \hfill            Summer 2008 \\
                Cross Rhythms Radio Station, Stoke-on-Trent
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Data entry into a large database.
	        \item Assisted with the successful running of their online e-commerce presence.
                 \end{itemize} 

	{\sl Studio Assistant} \hfill Summer 2007 \\
	Staffordshire University, Technology Department
	\begin{itemize} \itemsep -2pt
	\item Shadowed the technical managers of the music studios within the universities technology departments.
	\end{itemize}
        

\section{INTERESTS}             
           For as long as I can remember, I've had a genuine passion for computer science. I'm lucky
enough to be part of a generation where learning about new technologies is almost
instinct. Within the computer science field, I am highly enthusiastic about the Internet
and it's development. Several modules within my Computer Science course have enabled me to
understand how such a large scale network operates, and how to best utilise it to produce
high quality websites and applications.

I have been a keen musician for many years now, playing the trumpet to ABRSM Grade 7
standard, and the piano to Grade 4. These have both given me the opportunity to develop new
skills, build on my team working ability and to visit new places, having been on tours to
France, Spain and Germany in recent years. Before attending university, I was a member of
the Staffordshire North Youth Wind Orchestra and Staffordshire Moorlands Youth Jazz
Orchestra and I am now an enthusiastic member of the Aberystwyth Wind Orchestra.

When I manage to find spare time, I very much enjoy playing and
watching a variety of sports. I am a keen member of the Aberystwyth Squash Club, which
despite being a 1 vs. 1 game, requires a lot of team working to produce consistent
results. I also enjoy cricket, and played at club level before leaving home.

\section{REFERENCES}Harry Strange \hfill +44 (0)1970 628762, hgs08@aber.ac.uk\\
{\sl Research Associate \& First Year Tutor}\\ \\
Visualisation Building, Aberystwyth University, \\Aberystwyth, \\Ceredigion, \\SY23 2AX

\end{resume}
\end{document}







